### 2023-05-18 paper/content.tex

To simulate particles with non-dipole magnetization components, we specified a spherical volume with a radius of about 1 $\mu$m. Within this volume, we added 200 dipolar point particles with varying magnetization directions and magnetic moments. These directions were generated randomly to follow a normal distribution centered on the direction Dec=90°/Inc=0°, with a magnetic moment of $10^{-14}$ Am$^2$. We also randomly generated the spatial positions around a central position of $x_c=25~\mu$m, $y_c=25~\mu$m, and $z_c=\alpha~\mu$m, where $\alpha$ = 0, 1, ... 11 corresponds to the variation in depth of the particle. By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the Cartesian magnetization components for the spherical particle. The centroid of the particle was defined by the average of the $x_c$, $y_c$, and $z_c$ positions. The modeled vertical magnetic field was corrupted by a random noise of mean zero and a standard deviation of 20 nT.

According to Figure~\ref{non-dipolarity-synthetic-data} obtained from this simulation, it can be observed that when the particle is very close to the sensor, there is a strong non-dipolar contribution (Figure~\ref{non-dipolarity-synthetic-data}a-b) characterized by low $R^2$ values, indicating low dipolarity. As the distance increases, the magnetic signal is strongly attenuated, especially the non-dipolar components that decay more rapidly than the dipolar component, resulting in a rapid increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d). At distances above 5 $\mu$m, there is practically only the contribution of the dipolar component, causing $R^2$ values to be very close to 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).

@@

To assess the algorithm's capability to handle particles with more complex magnetization, we replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions. Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data. The effectiveness of position recovery was measured by comparing the particle's centroid with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively). As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero. However, when the sensor-source distance is small enough for there to be a strong contribution from higher-order components, a lower degree of dipolarity is observed, expressed as lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a). Consequently, in these cases, there are higher errors in the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which was expected since the inversion considers only the dipolar component. However, dipolarity significantly increases as the sensor distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).

>>>>

To simulate particles with non-dipole magnetization components, we specified a spherical volume with a radius of about 1 $\mu$m. Within this volume, we added 200 dipolar point particles with varying magnetization directions and magnetic moments. These directions were generated randomly to follow a normal distribution centered on the direction Dec=90°/Inc=0°, with a magnetic moment of $10^{-14}$ Am$^2$. We also randomly generated spatial positions around a central position of $x_c=25~\mu$m, $y_c=25~\mu$m, and $z_c=\alpha~\mu$m, where $\alpha$ = 0, 1, ... 11 corresponds to the variation in depth of the particle. By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the cartesian magnetization components for the spherical particle. The centroid of the particle was defined by the average of the $x_c$, $y_c$, and $z_c$ positions. The modeled vertical magnetic field was corrupted by a random noise of mean zero and a standard deviation of 20 nT.

According to Figure~\ref{non-dipolarity-synthetic-data} obtained from this simulation, it can be observed that when the particle is very close to the sensor, there is a strong non-dipolar contribution (Figure~\ref{non-dipolarity-synthetic-data}a-b) characterized by low $R^2$ values. As the distance increases, the magnetic signal is strongly attenuated, especially the non-dipolar components that decay more rapidly than the dipolar component, resulting in a rapid increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d). At distances above 5 $\mu$m, there is practically only the contribution of the dipolar component, causing $R^2$ values to be very close to 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).

@@

To assess the algorithm's capability to handle particles with more complex magnetization, we replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions. Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data. The effectiveness of position recovery was measured by comparing the particle's centroid with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively). As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero. However, when the sensor-source distance is small enough to emphasize the contribution from higher-order components, a lower degree of dipolarity is observed as expressed by lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a). Consequently, in these cases, there are higher errors in the estimation of the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which were expected since the inversion considers only the dipolar component. However, dipolarity significantly increases as the sensor to sample distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).
